Nix for Polyglot, Reproducible Data Science Workflows

### 2025-10-22 paper.qmd
Update paper.qmd
Update nixpkgs URL in CodeInput section

However, [renv]{.pkg} has important limitations. It does not restore the version
of [R]{.proglang} itself—installing the correct R version must be done
separately using tools like [rig]{.pkg} [@rlib2023]. More critically,
[renv]{.pkg} does not handle system-level dependencies. If [sf]{.pkg} requires
[GDAL]{.pkg} version 3.0 but the system has version 2.4 installed, [renv]{.pkg} cannot
resolve this conflict. Users must manually install system libraries, and the
process differs across operating systems. Further details are discussed in the
[renv]{.pkg} 
documentation^[\url{https://rstudio.github.io/renv/articles/renv.html#caveats}].

@@

```{=tex}
\begin{CodeInput}
$> nix-shell -I \
+  nixpkgs=https://github.com/rstats-on-nix/nixpkgs/archive/2025-10-20.tar.gz -p \
+  R rPackages.rix
\end{CodeInput}
```

>>>>

However, [renv]{.pkg} has important limitations. It does not restore the version
of [R]{.proglang} itself—installing the correct R version must be done
separately using tools like [rig]{.pkg} [@rlib2023]. More critically,
[renv]{.pkg} does not handle system-level dependencies. If [sf]{.pkg} requires
[GDAL]{.pkg} version 3.0 but the system has version 2.4 installed, [renv]{.pkg} cannot
resolve this conflict. Users must manually install system libraries, and the
process differs across operating systems. Further details are discussed in the
[[renv]{.pkg} documentation](https://rstudio.github.io/renv/articles/renv.html#caveats).

@@

```{=tex}
\begin{CodeInput}
$> nix-shell -I \
+  nixpkgs=https://github.com/rstats-on-nix/nixpkgs/tarball/2025-10-20 -p \
+  R rPackages.rix
\end{CodeInput}
```
